\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\title{Probability and Statistics: A Deep Refresher}

\newtheorem{exc}{Exercise}
\newtheorem{prb}{Problem}

\begin{document}
\maketitle
\tableofcontents
\part{Probability Theory}
\section{}

\subsection{Warm-up}
\begin{exc}
  How many different (and possible) combinations does a $3\times 3$ Rubik's cube have?
\end{exc}
\begin{exc}
  What is the probability of having a mono-colored face?
\end{exc}

What do you suggest for Rubik's cube's entropy? How much distance does it have from a solved cube?
Such an example would be 
\[ \sum (\mbox{\# of pairs of different colors on each face}). \]

Let's shuffle the cube randomly many times, and on each experiment, we count this entropy. As you see, this number is always (magically) near 60. Why?

\subsection{Some ancient problems}
\begin{prb} (Galileo)
  In tossing a die 3 times, is sum of 10 more probable or 9?
\end{prb}

\begin{prb}
  (Pascal's letter to Fermat) Consider these two gamblings: (1) We throw a die 4 times and bet on coming a 6. (2) We throw two dice 24 times and bet on a 6-6.

  Which gambling do you participate?
\end{prb}

\begin{prb}
  (Let's divide the prize) A chess game between players $A$ and $B$ is going on and the one who wins 5 times is going to be the winner. Because of some reasons, the game is halted in the state that $A$ has won 3 times and $B$ has won 2 times. What is the most fair way of dividing the first prize between $A$ and $B$?
\end{prb}

\begin{prb}
  The same problem, but put ``throwing a fair coin'' instead of playing chess. What will change?
\end{prb}

\begin{prb}
  (Laplace) If one has an unfair coin, what is the probability of heads in a throw?
\end{prb}

\subsection{Uniform distribution and Frequentist approach to probability}
blah blah blah

\subsection{De Finetti's view to probability}
blah blah blah

\part{Statistics}
\end{document}
